Data Mining in Nearby Galaxies

### 2016-07-04 main text/draft0.0.tex
Update draft0.0.tex
edits to summary. Removed phrases like "we concluded that.."

We present results of studying spatially resolved regions in nearby galaxies using 
The Self-organizing maps both cluster data and show relative distance between each cluster. 
Therefore, we utilized it to find hidden subgroups in the data as well as finding relation between those groups.

Using smaller-sized self-organizing maps, the M31 data are clustered into two major groups, which lead us to correlations that could not have otherwise been seen without clustering.
We found that six of the regions in M31 create a subgroup of data, that have relatively lower amount of Mid- and far-infrared emission.
PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and RHI.
These anti-correlations are insignificant when data from the whole galaxy are considered.
We discussed possible reasons for these anti-correlations and argued that the most probable reason to PAHs anti-correlate with optical emission and RHI is having harder radiation.
Harder radiation makes the size of H {\sc II} regions bigger and the size of PDRs smaller, which cause more \halpha~emission and less PAHs, respectively.

PAHs in clustered data also show anti-correlation with stellar mass.
We discussed the possibility of that higher stellar mass might destroy PAHs and as a result we see anti-correlation between them.
However, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
Unlike previous studies, we also did not find any correlation between 8/250~$\mu$m emission and stellar mass. 
This results show that PAHs in the clustered regions in M31, do not heated by old stellar populations.

In the maps with larger sizes, networks can be used to illustrate the relative relations of the regions with one another.
We found the relative similarity between M31 regions, by varying the size of networks.
A one-dimensional network with 14 neurons was needed in order to
separate all 10 regions; we concluded that some of the region in M31 (e.g. regions 4 and 7) have very similar properties.

A two-dimensional networks provide us a more complete picture of the data.
We created various subsets from input data and generated different networks which helped us to show a relative relations between regions in M31 more clearly.
We showed that region 10 always become isolated in networks, except when we only used PAHs data to create a network.
In that network region 10 blends more with other regions and only shows differences with data from region 8.
These results suggest that the PAHs in all 10 regions have almost the same properties.

% We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
% By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
We also applied the SOMs from M31 data to M101 data and found regions with similar properties in both galaxies placed in close regions in the SOMs.
We show that using this ability of the SOM, we can predict properties of regions in other nearby galaxies very fast.
We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
Increasing dimension of the data and the number of regions would help to have more reliable networks.
In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83), and learn about the properties of regions on those galaxies.

\section*{ACKNOWLEDGMENTS}
The authors thank A. Tammour for her useful comments. 
S.R., P.B., and E.P. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mn2e}
\bibliography{ref_mining.bib}
\import{../sections/}{app_2d.tex}

>>>>

We present results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
Self-organizing maps both cluster data and show relative distance between the clusters. 
We utilized the method to find hidden subgroups in the data as well as finding relations between those groups.

Using smaller-sized self-organizing maps, we found that the M31 data are clustered into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
These anti-correlations are insignificant when the full dataset is considered.
The most probable reason for PAHs to anti-correlate with optical emission line and RHI is a harder radiation field.
This makes the size of H {\sc II} regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.

PAHs in clustered data also show an anti-correlation with stellar mass.
We discussed the possibility that higher stellar mass might destroy PAHs;
however, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
Unlike previous studies, we also did not find any correlation between 8/250~$\mu$m emission and stellar mass. 
This result shows that PAHs in the clustered regions in M31 are not heated by the old stellar populations.

In self-organizing maps with larger sizes, networks can be used to illustrate the relations of the regions with one another.
We found the relative similarity between M31 regions by varying the size of the networks.
A one-dimensional network with 14 neurons was needed in order to
separate all 10 regions; some of the regions in M31 (e.g. regions 4 and 7) have very similar properties.
% PB joining paragraphs
Two-dimensional networks provide us with a more complete picture of the data.
We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
Region 10 always becomes isolated in the networks, except when we  used only PAH data to create a network. %PB: remind the reader where regions 8 and 10 are
In that network region 10 blends more with other regions and only shows differences with the data from region 8.
These results suggest that the PAHs in all 10 regions have almost the same properties.

% We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
% By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
Applying the SOMs from M31 to observations of M101, we found regions with similar properties in both galaxies placed in close regions in the SOMs.
Using this ability of the SOM, we can predict properties of regions in other nearby galaxies very quickly.
The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
Increasing the dimension of the data and the number of regions would yield more reliable networks.
In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83) and learn about the properties of regions in those galaxies.

\section*{ACKNOWLEDGMENTS}
The authors thank Dr A.\ Tammour for useful comments. 
S.R., P.B., and E.P. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mn2e}
\bibliography{ref_mining.bib}
\import{../sections/}{app_2d.tex}
